---
title: "ggplot(datacamp)"
author: "fat guy"
date: "2018/02/16"
output:
  html_document:
    toc : true
    toc_depth: 3
    toc_float: 
      collapsed: false
      smooth_scroll: false
---

<font color="red" size = 24> data "mtcars" is preloaded in R </font>
<font color="red" size = 24> data "diamonds" is preloaded in R </font>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




##compare this two commands with `factor()` inside `aes()`

Change the command so that cyl is treated as factor

```{r}
library(ggplot2)

ggplot(mtcars, aes(x = cyl, y = mpg)) +
  geom_point()
ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_point()
```




##compare color and size in `aes()`

furthermore, `geom_point()` + `geom_smooth()` are common combination

```{r}
ggplot(mtcars, aes(x = wt, y = mpg, color = disp)) +
  geom_point() + geom_smooth()

ggplot(mtcars, aes(x = wt, y = mpg, size = disp)) +
  geom_point()
```




##a continuous variable cant not be mapped to shape

"shape" only makes sense with categorical data, and "disp" is continuous.

```{r}
#ggplot(mtcars, aes(x = wt, y = mpg, shape = disp)) +
#  geom_point()
ggplot(mtcars, aes(x = wt, y = mpg, shape = factor(disp))) +
  geom_point()
```




##clarity mapped to color
```{r}
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) +
  geom_smooth()
```




##transparent

Set "alpha ="  inside `geom_point()`. This will make the points 40%/20% transparent.

```{r}
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) +
  geom_point()
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) +
  geom_point(alpha = 0.4)
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) +
  geom_point(alpha = 0.2)
```




##`aes()` can also be uesd in `geom_point()` etc..

Note that you can also call `aes()` within the `geom_point()` function.

furthermore, "se = " can display the smooth around the smooth(TRUE by default)

complete themes : http://ggplot2.tidyverse.org/reference/ggtheme.html

```{r}
ggplot(diamonds, aes(x = carat, y = price)) + geom_point()
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) + geom_point()
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) + geom_point() + theme_minimal()
ggplot(diamonds, aes(x = carat, y = price)) + geom_point(aes(color = clarity))
ggplot(diamonds, aes(x = carat, y = price)) + geom_point() + 
  geom_smooth(aes(color = clarity))
ggplot(diamonds, aes(x = carat, y = price)) + geom_point() + 
  geom_smooth(aes(color = clarity, se = FALSE))
```




#probability desity function
```{r}
#ggplot(airquality, aes(x = Temp, color = Month)) +  geom_density()
```

