---
title: "markdown practice"
author: "fat guy"
date: "2018/01/22"
output:
  html_document:
    toc : true
    toc_depth: 3
    toc_float: 
      collapsed: false
      smooth_scroll: false
  pdf_document: default
  word_document: default
---

R Markdown sent back both result and code to the console as a default `include = TRUE`

`include = FALSE` : will not display neither result nor code

`echo = FLASE` : display the result, the code will be hid

`result = "hide"` : display the code, the result will be hid


press ctrl + alt + I to generate a new chunk

```{r setup, include=FALSE} 
# chunk setting ¡ô
knitr::opts_chunk$set(echo = TRUE) #global setting
# options(knitr.table.format = "html")
```


# Cars

```{r}
summary(cars) #include = TRUE #default
```
```{r, include = FALSE}
summary(cars) #include = FALSE #we had neither code nor output(result)
```
```{r, echo = FALSE}
summary(cars) #echo = FALSE #only result
```
```{r, results = "hide"}
summary(cars) #results = "hide" #only code
```

# Pressure

```{r}
plot(pressure)
```

# Mixed Code and Text in the Same Paragraph

we want to create a sequence using `seq()` fuction



# Advanced Chunk Argument Setting 

### set chunk by chunk

```{r, echo = FALSE, fig.width = 4, fig.height = 2.5}
plot(cars)
```

### we can set argument via global chunk

```{r, include = FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 5)
```
```{r}
plot(cars)
```


# Table

### default

Function `kable()` can list all data at below
```{r}
library(knitr)
kable(cars)
```

### kable(tidy data)

```{r}
library(knitr)
kable(iris)
```

### limit the table to a fixed height

```{r}
library(knitr)
library(dplyr)
library(kableExtra)
cars %>% kable("html") %>% scroll_box(height = "500px", width = "500px")
```

