---
title: "R practice"
author: "fat guy"
date: "2018/02/16"
output:
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: no
      smooth_scroll: no
  word_document:
    toc: yes
    toc_depth: '6'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
```




#function

##paste and append

paste for character

append for vector

data can be a 5*n matrix, n is a positive integer

we can give the column names by using `colnames()`

```{r}
library(magrittr)
nms <- paste("year_", 1:153)
nms
nms1 <- paste("year_", 1:5, sep = ",")
nms1
nms0 <- paste0("year_", 1:5)
nms0
e <- airquality$Wind %>% as.matrix()
rownames(e) <- nms
e
paste(iris$Sepal.Length, cars$speed) #compare two data
paste(iris$Sepal.Length, cars$speed, sep = "vs")
append(iris$Sepal.Length, cars$speed) #append another data
```




##sample, sort and order
```{r}
c <- sample(1:100, size = 20)
sort(c, decreasing = TRUE)
order(c, decreasing = TRUE)
c[order(c, decreasing = TRUE)]
```




##unique and duplicate

unique : exract the elements from data

duplicated : test the repetition, return TURE if the duplicate data show behind
```{r}
unique(cars$dist)
duplicated(cars$dist) %>% table()
```




##which
```{r}
which(airquality$Month == 5)
```




##furthermore
http://www3.nccu.edu.tw/~99354011/R%20commands%2811.09.13%29.pdf




#data visualiztion

##build histogram

breaks : the n+1 cell boundaries (= breaks if that was a vector). These are the nominal breaks, not with the boundary fuzz.

```{r}
#Build histogram of data
hist(cars$dist, breaks = 5) #e.g. 1,2,3,4,5,6,7,8........
hist(cars$dist, breaks = 10)
```




#logical operator

Next to relational operators, there are also logical operators

& : AND

| : OR

! : NOT

==、!= ：等於、不等於

A %in% B ：A 是否在 B 中

&&、＆ : 交集，& 適用於向量式的邏輯判斷，&& 適用於單一值的邏輯判斷

||、| ：聯集，| 適用狀況與 & 相同，|| 適用狀況與 && 相同

```{r}
# e.g.What's the proportion of dist in data cars that is greater than or equal to 70 and lower than or equal to 85?
mean(cars$dist >= 70 & cars$dist <= 85)

# e.g.How many cars had a dist of 34 or 40?
sum(cars$dist == 34 | cars$dist == 40)
```




#process control

##if, else
```{r}
a <- 99
if (a > 70) {
  print("乖")
} else {
  print("重修吧你")
}
```

```{r}
ifelse(a > 70, "乖", "重修吧幹")
```

```{r}
if (a > 70) "乖" else "重修吧廢"
```




##if, else if, else
```{r}
b <- mean(cars$dist)
if (b > 0.9) {
  print("nice")
} else if (prop_less > 0.8 & prop_less <= 0.9) {
  print("its ok")
} else {
  print("垃圾")
}
```




##if & else, if & else
```{r}
me <- 89
classmean <- 75.515
if (classmean > 75) {
  if(classmean > me) {
    print("66666")
  } else {
    print("7777")
  }
} else {
  if (classmean > me){
    print("i am fat guy")
  } else {
    print("嘻嘻嘻")
  }
}
```

```{r}
me <- 89
classmean <- 75.515
if (classmean > 75) 
{
  if(classmean > me) 
  {
    print("66666")
  } else 
  {
    print("7777")
  }
} else 
{
  if (classmean > me)
  {
    print("i am fat guy")
  } else 
  {
    print("嘻嘻嘻")
  }
}
```


QZWD

## if
```{r}
d <- cars$dist[cars$dist < 65]
s <- cars$speed[cars$speed > 5 | cars$speed > 14]
if (length(d) - length(s) < 0) {
  print("fat guy")
}
```




##switch
```{r}
switch(1, 1+1, 2+1, 3+1)
switch(2, 1+1, 2+1, 3+1)
switch("fatguy", fat = 100, fatguy = "me")
```




##switch & if else
```{r}
a <- 99
switch( if (a > 90) 1 else 2, 1+1, 2+2 )

switch( ifelse (a > 90, 1, 2), 3+3, 4+4)

switch( if ( a > 90 )  { 1
         } else { 2
             }, 5+5, 6+6
       )
```




#loop

##for
```{r}
y <- 0
for ( x in c(1:10) ) y <- x + y
y; sum(y); print(y)

y <- 0
for ( x in c(1:10) ) {
  y <- x + y
}
y

y <-0
for (x in 1:10 ) y <- x + y
y

y <- 0
for ( x in c(1:10) ) z <- x + y
z; sum(z); print(z)

y <- 0
for ( x in c(1:10000000) ) {
  z <- x + y
}
z

```




##while
```{r}
x <- 1
y <- 0
while (x <= 17) {
  y = y + x #1加到17的意思
  x = x + 1 #防止無窮迴圈
}
y #1加到17=210
x #17+1(最後一個)


x <- 1
y <- 0
while (x <= 1700000) {
  if(x > 9) break
  y = y + x
  x = x + 1
}
y #1加到9=45
x #break when x > 9, thus x = 9 + 1
```




##repeat & break
```{r}
x <- 0
y <- 1
repeat { #more free than while~~~~~~
  if (y > 9) break # "break" means "stop"
  x = y + x
  y = y + 1
}
x
y
```




##while/repeat & break
```{r}
#now, want to calculate summation from 1 to 20 except 6 
x <- 0
y <- 0
repeat {
  if(x > 20) {
    break
  } else if (x == 6) {
    x <- x + 1 #if omit this code, infinite loop will be occured
    next
  }
  y <-  x + y
  x <-  x + 1
}
y
x
```




# apply

`lapply`的第一個參數`X`通常是一個vector。 第二個參數`FUN`則是代表一種「動作」。 `lapply`會對每一個`X`的元素進行`FUN`所定義的動作，並且把結果彙整回R之中。

lapply returns a list of the same length as X, each element of which is the result of applying FUN to the corresponding element of X.

另外一種方式是使用`sapply`這個函數。 `sapply`和`lapply`幾乎一樣，差別在於`sapply`最後會嘗試重新整理輸出的格式，將list轉成array。請同學試試`sapply(tmp, "[", 1)`。

當我們想要從文字中擷取出資訊時，都可以優先考慮運用`substring`或`strsplit`來擷取資訊。 而當R將資訊轉成非結構化的list物件後，可以運用`lapply`或`sapply`做資料的整理。

http://127.0.0.1:21205/library/base/html/lapply.html

##apply & supply
```{r}
iris$Sepal.Width

library(knitr)
library(kableExtra)
lapply(iris$Sepal.Width, "+", 1) %>% kable("html") %>% scroll_box(height = "500px", width = "500px")

sapply(iris$Sepal.Width, "+", 1)
```




#processing data

##missing value
```{r}
table(is.na(airquality))
library(magrittr)
library(knitr)
library(kableExtra)
airquality %>% is.na() %>% kable("html") %>% scroll_box(height = "500px")
#如何看每一欄有幾個na?
na.omit(airquality) %>% kable("html") %>% scroll_box(height = "500px")
```




##NA
```{r}
airquality <- airquality

library(magrittr)
is.na(airquality$Ozone) %>% sum()
airquality$Ozone[airquality$Ozone == "NA"] #this code is equal to the following code
airquality[is.na(airquality$Ozone), 1]
#and compare with the follwing code
airquality[is.na(airquality$Ozone), 2]
airquality[is.na(airquality$Ozone), 3]

#more example
airquality[is.na(airquality$Solar.R), 1]
airquality[is.na(airquality$Solar.R), 2]
airquality[is.na(airquality$Solar.R), 3]
```




## `[]` and `[[]]`

x[i]：回傳向量元素所有資訊
x[[i]]：只回傳向量元素的值
x[元素名稱]：回傳向量元素所有資訊
x[[元素名稱]]：只回傳向量元素的值

```{r}
library(dplyr)
library(knitr)
library(kableExtra)
iris[1] %>% kable("html") %>% scroll_box(height = "250px", width = "500px")
iris[[1]] %>% kable("html") %>% scroll_box(height = "250px", width = "500px")

airquality["Wind"] %>% kable("html") %>% scroll_box(height = "250px", width = "500px")  #"element's name"
airquality[["Wind"]] %>% kable("html") %>% scroll_box(height = "250px", width = "500px")

iris[2:5,1:3]
```




##array, aperm and dim
```{r}
array(iris$Petal.Length, c(3, 4)) #generating a 3*4 array

array(iris$Sepal.Width, c(5, 8)) %>% aperm() #a 8*5 matrix
```




##input data (iconv : convert the encoding)

iconv(data, "big5", "utf8") convert the encoding of data to UTF-8




##output data
```{r}
setwd("C:/Users/USER/Downloads/")
write.csv(iris, file = "iris.csv")
getwd()
```




##recode
```{r}
library(magrittr)
mtcars <- mtcars
mtcars %>% class()
median(mtcars$disp)
repeat {
  if (median(mtcars$disp) == 0 | median(mtcars$disp) == 0.5 | median(mtcars$disp) == 1) break
  mtcars$disp <- ifelse(mtcars$disp >196.3, 1, 0)
}
mtcars$disp


mtcars <- datasets::mtcars
if (median(mtcars$disp) == 0.5 | median(mtcars$disp) == 0 | median(mtcars$disp) == 1) {
   print("done")
} else {
   mtcars$disp <- ifelse (mtcars$disp > 196.3, 1, 0)
} 
mtcars$disp
```

```{r}
library(magrittr)
ToothGrowth <- ToothGrowth
ToothGrowth %>% class()
ToothGrowth$supp <-  ifelse(ToothGrowth$supp %in% "VC", "isVChaha", "notVC QAQ")

iris <- iris
iris$Species <- ifelse(iris$Species %in% "setosa", "IsSetosa","Notsetosa")
```




##reshape
```{r}
library(magrittr)
iris1 <- iris %>% stack()
iris1
#iris2 <- iris %>% unstack() #???
#iris2
```

```{r}
library(longitudinalData) #???
#iris4 <- iris
#iris4 <- longitudinalData::artificialJointLongData

#data_long <- reshape(iris4, direction="long", varying = list(c("v0", "v1", "v2", "v3", "v4", "v5", "v6", "v7", "v8", "v9", "v10"), c("w0", "w1", "w2", "w3", "w4", "w5", "w6", "w7", "w8", "w9", "w10"), c("x0", "x1", "x2", "x3", "x4", "x5", "x6", "x7", "x8", "x9", "x10")), v.names = c("v", "w", "x"), idvar = "id")

#data_wide <- reshape(data_long, direction="wide",v.names = c("v", "w", "x"), idvar = "id")

```

want to know how many NA in column, respectively
```{r}
airquality <- airquality

library(tidyr)
airquality <- airquality %>% gather(columnname, value) #convert wide format data to long format data

library(dplyr)
#sum(airquality$value == "NA") faliure, refer the following code
sum(is.na(airquality$value))
airquality[is.na(airquality$value), 2] <- 0
airquality %>% filter(value == 0) %>%  group_by(columnname) %>% summarise("NA"=n()) %>% View()
```




##data combination
```{r}
ept1 <- list(names = c("tung", "long", "fatguy"), cm = c(18, 3, 20))
ept2 <- list(sport = c("大肌肌", "LOL", "肥宅不運動"), sport_time = c(20, 24, 0))
library(magrittr)
ept12_1 <- cbind(ept1$names, ept2$sport_time) %>% as.data.frame()
class(ept12_1)
colnames(ept12_1) <- c("names", "sport_time")
ept12_1

ept12_2 <- cbind(ept1$names, ept2$sport, ept2$sport_time)
class(ept12_2)
colnames(ept12_2) <- c("names", "sport", "sport_time")
ept12_2
```

```{r}
ept3 <- cbind(names = c("tung", "long", "fatguy"), cm = c(18, 3, 20)) %>% as.data.frame()
ept4 <- cbind(c("大肌肌", "LOL", "肥宅不運動"), c(20, 24, 0)) %>% as.data.frame()
colnames(ept4) <- c("sport", "sport_time")
ept34_1 <- cbind(ept3, ept4)
ept34_2 <- merge(ept3, ept4) #這裡不適合

ept5 <- cbind(names = c("tung", "long", "fatguy"), cm = c(18, 3, 20))
ept6 <- cbind(names = c("tung", "long", "fatguy"), sport = c("大肌肌", "LOL", "肥宅不運動"), sport_time = c(20, 24, 0))
ept56_1 <- merge(ept5, ept6, by = "names") #有相同的column name
ept56_2 <- merge(ept5, ept6)
```




##data partition
```{r}
iris <- iris
rep(1:11, 3)
sample(50000, 100) #50000 隨機 再抽樣 (抽100個)
sample(rep(1:11, 5)) #1:11重複5次 再抽樣
sample(rep(1:11, 5), 50) #1:11重複5次 再抽樣 (抽50個)

set.seed(1234)
iris0 <- split(iris, c(10, 25, 55, 9999)) #split依照10,25,55,9999分組 因此最大資料可取用量 為4組, 若是iris0[[5]]則無法取得
iris1 <- split(iris, sample(rep(1:15, 100))) #split會分組 因為1:15 所以共分成15組 因此最大資料可取用量 為15組, 若是iris1[[16]]則無法取得
iris1_1 <- iris1[[1]] #取第一組
iris1_2 <- iris1[[2]] #取第二組
iris1_3 <- iris1[[3]] #取第三組
length(iris1_1$Sepal.Length)
length(iris1_2$Sepal.Length)
length(iris1_3$Sepal.Length)

iris <- iris
subset(iris$Sepal.Width, iris$Sepal.Width > median(iris$Sepal.Width))
median(iris$Sepal.Length)
median(iris$Sepal.Width)
iris2_1 <- subset(iris, Sepal.Length > 5.8, Sepal.Width) #this code is euqal to the following code
iris2_2 <- subset(iris, Sepal.Length > 5.8, select = Sepal.Width)
iris2_3 <- subset(iris, Sepal.Length > 5.8, select = -Sepal.Width)

iris <- iris
#compare following four codes
iris3_1 <- subset(iris, Sepal.Length > 5.8 & Sepal.Width)
iris3_2 <- subset(iris, Sepal.Length > 5.8 & Petal.Length)
iris3_3 <- subset(iris, Sepal.Length > 5.8 & Petal.Width)
iris3_4 <- subset(iris, Sepal.Length > 5.8)

iris <- iris
iris4_1 <- subset(iris, Sepal.Length > 5.8 & Sepal.Width > 3)
```




##custom function
```{r}
cal1_1 <- function(a, b, c){
  (a+b) / c
}
cal1_1(2, 3, 4)

cal1_2 <- function(a = 1, w, m){
  (a+w) * m
}
cal1_2(w = 1, m = 3) #with default a
cal1_2(w = 2, m = 3) #with default a
cal1_2(a = 5, w = 1, m = 3)
cal1_2(a = 5, w = 2, m = 3)


#compare the following three customized functio
cal2_1 <- function(a, b, c){
  d = (a+b) / c
}
cal2_1(2, 3, 4) #no value

cal2_2 <- function(a, b, c){
  d = (a+b) / c
  return(d) #we can choose the value which we want to return ; in here, d
}
cal2_2(2, 3, 4)

cal2_3 <- function(a, b, c){
  d = (a+b) / c
  return(0) #we can choose the value which we want to return ; in here, 0 
}
cal2_3(2, 3, 4)
```




#database

##read data from database

use <font color="green">DBI, gWidgets, RMySQL and dbConnect</font> to read data from database, the following is to read data from <font color="blue">MySQL</font> database as an example

```{r, include = FALSE}
library(DBI)
library(gWidgets)
library(RMySQL)
library(dbConnect)

#house1 <- dbConnect(MySQL(), dbname = "house_development", password = "123456", username = "root", host = "localhost")

#dbSendQuery(house1, "SET NAMES big5") # 設定BIG-5防止亂碼

#dbGetQuery(house1, "show variables like 'character_%'") # '' 內是VARIABLE顯示出來的形式

#db_list_tables(house1) 

#house <- dbGetQuery(house, "select * from house") # 讀取資料
```




#statistics

##linear regression

build regression

```{r}
library(dplyr)
f <- lm(data = iris, Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width) %>% summary()
f
```


`shapiro.test()` can test the normality of residual

```{r}
f$residuals %>% kable("html") %>% scroll_box(height = "500px")
shapiro.test(f$residuals)
#do not reject Ho
```


`durbinwatsontest()` is a test of Independence or residual

```{r}
library(car)
durbinWatsonTest(lm(data = iris, Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width))
#do not reject Ho
```


function `ncvTest()` in package "car" is a tset of homogenity of variance

```{r}
ncvTest(lm(data = iris, Sepal.Length ~ Sepal.Width + Petal.Length + Petal.Width))
#reject Ho
```




##combination & permutation
```{r}
choose(5, 2)
choose(100, 5)

#permutation?
```
























































